---
title: "Sharp Bounds for Continuous-Valued Treatment Effects with Unobserved Confounders"
author: "Jean-Baptiste BAITAIRIAN"
date: "2024-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Import libraries
library(ggplot2)    # For figures
library(foreach)    # For "for" loops
library(torch)      # For neural networks
library(latex2exp)  # For LaTeX expressions
library(tictoc)     # For computation times

# Import R files
source("./utils.R")
```

```{r}
# Set random seed
seed <- 1
set.seed(seed)
torch_manual_seed(seed)
```

```{r}
# Colors for the plots
our_method_blue <- "#00BFC4"
our_method_dr_yellow <- "#C9A100"
jesson_red <- "#F8766D"
apo_color <- "violetred3"
```


## Simulated dataset

Example of one Monte-Carlo sample with the true APO curve.
```{r, fig.width = 7.06, fig.height = 5.72}
# Sample size
n <- 1000

# Number of confounders
p_X <- 5
p_U <- 3

# Correlation between confounders
rho_X <- 0.3
rho_U <- 0.3
corr_XU_prop <- 0.5  # 0.05

beta_X <- rep(0.3, p_X)
beta_U <- rep(0.2, p_U)

gamma_X <- rep(0.2, p_X)
gamma_U <- c(rep(0.4, floor(p_U/2)), rep(0.7, p_U-floor(p_U/2)))
zeta <- -0.3

sd_eps_T <- 0.5
sd_eps_Y <- 0.3

simu <- simulated_dataset(n=n, p_X=p_X, p_U=p_U,
                          rho_X=rho_X, rho_U=rho_U,
                          corr_XU_prop=corr_XU_prop,
                          beta_X=beta_X, beta_U=beta_U,
                          gamma_X=gamma_X, gamma_U=gamma_U,
                          zeta=zeta, sd_eps_T=sd_eps_T, sd_eps_Y=sd_eps_Y)

n.effective <- nrow(simu$data)

grid_t <- seq(min(simu$data$t), max(simu$data$t), 0.1)
cov_XU <- simu$cov_XU
Sigma_X <- simu$Sigma_X

X <- subset(simu$data, select=-c(Y, t))
t <- simu$data$t
Y <- simu$data$Y

apo_for_plot_fun <- function(t) apo_t(t=t, zeta=zeta,
                                      gamma_X=gamma_X, gamma_U=gamma_U,
                                      cov_XU=cov_XU, Sigma_X=Sigma_X)

# Plot simulated data
# png("images/simul_data.png", units="in", width=7.06, height=5.72, res=400)
simul.data.plot <- ggplot(data.frame(t=t, Y=Y, apo=apo_for_plot_fun(t))) +
  geom_point(aes(x=t, y=Y)) +
  geom_line(aes(x=t, y=apo), col=apo_color, linewidth=1.1) +
  theme_linedraw() +
  labs(x=TeX(r"(Treatment or exposition $\tau$)"), y="Outcome Y") +
  annotate("text", x=2.4, y=3.5, label=TeX(r"($\theta(\tau)$)"), colour=apo_color, size=7, parse=TRUE)
simul.data.plot
# dev.off()
```

### Sensitivity analysis for 5 values of expositions, to compare the proposed methodology to Jesson et al. (2022)

```{r}
# 1: parallel.computation.jesson (boolean)
# 2: n.MC (1:infty)
# 3: data.name ("simul" or "cmr")
# 4: gamma_est, for cmr data (real number from 1 to 50) 
# 5: xi.method (NULL or "neural_network")
# 6: compute.jesson (boolean)
# 7: doses.length (2:infty)
# 8: version (1:infty)
commandArgs <- function(...) c(TRUE, 20, "simul", 1, "NULL", TRUE, 5, 1)
source("./sens_analys_MC_cmr_and_simu.R")
```

```{r}
commandArgs <- function(...) c(FALSE, 20, "simul", 1, "neural_network", FALSE, 5, 2)
source("./sens_analys_MC_cmr_and_simu.R")
```

```{r}
version <- "v1"

qb.mc.bounds <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version, ".RData"))
qb.exec.times <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version, ".RData"))
qb.cov <- readRDS(paste0("results/qb_simul_cov_B_100_", version, ".RData"))

jesson.mc.bounds <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version, ".RData"))
jesson.exec.times <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version, ".RData"))
jesson.cov <- readRDS(paste0("results/jesson_simul_cov_B_100_", version, ".RData"))

gammas <- readRDS(paste0("results/gammas_simul_", version, ".RData"))
```

```{r}
version2 <- "v2"

qb.mc.bounds2 <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version2, ".RData"))
qb.exec.times2 <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version2, ".RData"))
qb.cov2 <- readRDS(paste0("results/qb_simul_cov_B_100_", version2, ".RData"))

jesson.mc.bounds2 <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version2, ".RData"))
jesson.exec.times2 <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version2, ".RData"))
jesson.cov2 <- readRDS(paste0("results/jesson_simul_cov_B_100_", version2, ".RData"))

gammas2 <- readRDS(paste0("results/gammas_simul_", version2, ".RData"))
```

```{r}
n.MC <- length(qb.mc.bounds)
doses.length <- length(qb.mc.bounds[[1]]$dose) / 2
quant.order <- 0.99


# Compute the mean coverage for each Monte-Carlo sample
qb.coverage.vec <- rep(NA, n.MC)
jesson.coverage.vec <- rep(NA, n.MC)
# the mean CI length
qb.CI.length.vec <- rep(NA, n.MC)
jesson.CI.length.vec <- rep(NA, n.MC)
# and the mean PEI length
qb.PEI.length.vec <- rep(NA, n.MC)
jesson.PEI.length.vec <- rep(NA, n.MC)

other.qb.df <- NULL
other.jesson.df <- NULL

other.qb.df2 <- NULL
other.jesson.df2 <- NULL

for (i in 1:n.MC) {
  
  # For continuous QB
  qb.mc.bounds.i <- qb.mc.bounds[[i]]
  qb.mc.bounds.i.ci <- qb.mc.bounds.i[qb.mc.bounds.i$type == "CI", ]
  qb.mc.bounds.i.pei <- qb.mc.bounds.i[qb.mc.bounds.i$type == "PEI", ]
  
  qb.coverage.vec[i] <- mean(qb.mc.bounds.i.ci$lb <= qb.mc.bounds.i.ci$apo & qb.mc.bounds.i.ci$apo <= qb.mc.bounds.i.ci$ub)
  qb.CI.length.vec[i] <- mean(qb.mc.bounds.i.ci$ub - qb.mc.bounds.i.ci$lb)
  qb.PEI.length.vec[i] <- mean(qb.mc.bounds.i.pei$ub - qb.mc.bounds.i.pei$lb)
  
  qb.mc.bounds.i$MC.ind <- i
  other.qb.df <- rbind(other.qb.df, qb.mc.bounds.i)
  
  qb.mc.bounds.i2 <- qb.mc.bounds2[[i]]
  qb.mc.bounds.i2$MC.ind <- i
  other.qb.df2 <- rbind(other.qb.df2, qb.mc.bounds.i2)
  
  # For Jesson
  jesson.mc.bounds.i <- jesson.mc.bounds[[i]]
  jesson.mc.bounds.i.ci <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "CI", ]
  jesson.mc.bounds.i.pei <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "PEI", ]
  
  jesson.coverage.vec[i] <- mean(jesson.mc.bounds.i.ci$lb <= jesson.mc.bounds.i.ci$apo & jesson.mc.bounds.i.ci$apo <= jesson.mc.bounds.i.ci$ub)
  jesson.CI.length.vec[i] <- mean(jesson.mc.bounds.i.ci$ub - jesson.mc.bounds.i.ci$lb)
  jesson.PEI.length.vec[i] <- mean(jesson.mc.bounds.i.pei$ub - jesson.mc.bounds.i.pei$lb)
  
  jesson.mc.bounds.i$MC.ind <- i
  other.jesson.df <- rbind(other.jesson.df, jesson.mc.bounds.i)
  
  jesson.mc.bounds.i2 <- jesson.mc.bounds2[[i]]
  jesson.mc.bounds.i2$MC.ind <- i
  other.jesson.df2 <- rbind(other.jesson.df2, jesson.mc.bounds.i2)
}
```

```{r}
other.qb.df2$method <- "Proposed method (DR)"
ci.data <- rbind(other.qb.df, other.qb.df2, other.jesson.df)
ci.data <- ci.data[ci.data$type == "CI", ]

ci.data[ci.data$method == "Continuous SAIPW-QB", ]$method <- "Proposed method"
ci.data[ci.data$method == "Jesson et al.", ]$method <- "Jesson et al. (2022)"
ci.data$method <- factor(ci.data$method, levels=c("Proposed method", "Proposed method (DR)", "Jesson et al. (2022)"))

# png("images/simul_sens_anal_20MC.png", units="in", width=6.68, height=5.72, res=400)
# Plot the CI boxplots to compare Jesson et al. to our method and our DR estimator
ci.simu.comparison.plot <- ggplot(ci.data) +
  geom_boxplot(aes(x=factor(signif(dose, 3)), y=lb, fill=method), fatten=TRUE, width=0.4, outlier.shape=NA) +
  geom_boxplot(aes(x=factor(signif(dose, 3)), y=ub, fill=method), fatten=TRUE, width=0.4, outlier.shape=NA) +
  geom_point(aes(x=factor(signif(dose, 3)), y=apo, group=1), shape=18, size=3, color=apo_color) +
  scale_fill_manual(values=c(our_method_blue, our_method_dr_yellow, jesson_red), breaks=c("Proposed method", "Proposed method (DR)", "Jesson et al. (2022)")) +
  labs(fill="Method", x=TeX(r"(Treatment or exposition $\tau$)"), y="Outcome Y") +
  theme_linedraw() +
  theme(legend.position=c(0.81, 0.15), legend.background=element_rect(size=0.3, linetype="solid", colour="black"),
        axis.title.x=element_text(size=12),
        axis.title.y=element_text(size=12),
        axis.text=element_text(size=10),
        legend.text=element_text(size=11),
        legend.title=element_text(size=12),
        panel.grid.major.x=element_blank()) +
  annotate("text", x=5.2, y=1.55, label=TeX(r"($\theta(\tau)$)"), colour=apo_color, size=5, parse=TRUE)
ci.simu.comparison.plot
# dev.off()
```

### Sensitivity analysis on 1 MC sample with our method

```{r}
commandArgs <- function(...) c(FALSE, 1, "simul", 1, "NULL", FALSE, 15, 3)
source("./sens_analys_MC_cmr_and_simu.R")
```

```{r}
version <- "v3"

qb.mc.bounds <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version, ".RData"))
qb.exec.times <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version, ".RData"))
qb.cov <- readRDS(paste0("results/qb_simul_cov_B_100_", version, ".RData"))

jesson.mc.bounds <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version, ".RData"))
jesson.exec.times <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version, ".RData"))
jesson.cov <- readRDS(paste0("results/jesson_simul_cov_B_100_", version, ".RData"))

gammas <- readRDS(paste0("results/gammas_simul_", version, ".RData"))

observed.data.df <- data.frame(lb=NA, ub=NA, unconf=NA,
                               apo=rep(apo_for_plot_fun(t), 2),
                               dose=rep(t, 2),
                               name=NA, method=NA,
                               type=c(rep("PEI", nrow(X)), rep("CI", nrow(X))),
                               y.observed=rep(Y, 2))

type.labs <- c("Confidence Interval", "Point Estimate Interval")
names(type.labs) <- c("CI", "PEI")

qb.df.plot <- qb.mc.bounds[[1]]
qb.df.plot$y.observed <- NA
```

```{r, fig.width = 7.69, fig.height = 4.54}
# Plot with both intervals on one graph
# png("images/simul_sens_anal_PEI_CI_1MC.png", units="in", width=7.69, height=4.54, res=400)
simul.pei.ci.plot <- ggplot(data=qb.df.plot) +
  geom_point(data=observed.data.df, aes(x=dose, y=y.observed), colour="#EEEEEE") +
  geom_ribbon(aes(ymin=lb, ymax=ub, x=dose, fill=type, colour=type), alpha=0.25) +
  geom_line(aes(x=dose, y=unconf), linetype="dashed", col=our_method_blue, linewidth=0.7) +
  geom_line(data=observed.data.df, aes(x=dose, y=apo), col=apo_color, linewidth=0.5) +
  scale_x_continuous(breaks=unique(qb.df.plot$dose),
                     labels=round(unique(qb.df.plot$dose), 2),
                     limits=c(min(unique(qb.df.plot$dose))-0.2, max(unique(qb.df.plot$dose))+0.2)) +
  scale_fill_discrete(guide="legend", name="Interval type", labels=type.labs) +
  scale_color_discrete(guide="legend", name="Interval type", labels=type.labs) +
  theme_linedraw() +
  labs(x=TeX(paste("Treatment or exposition", r"($\tau$)")),
       y="Outcome Y") +
  theme(legend.position=c(0.87, 0.13), legend.background=element_rect(size=0.3, linetype="solid", colour="black")) +
  annotate("text", x=1.83, y=2.4, label=TeX(r"($\theta(\tau)$)"), colour=apo_color, size=5, parse=TRUE) +
  annotate("text", x=1.83, y=1.2, label="widehat(theta)(tau)", colour=our_method_blue, size=5, parse=TRUE)
simul.pei.ci.plot
# dev.off()
```

### Execution times for sensitivity analyses with 2, 3 and 4 values of treatment of interest (proposed method and Jesson et al. (2022) without parallel computing)

```{r}
# 1: parallel.computation.jesson (boolean)
# 2: n.MC (1:infty)
# 3: data.name ("simul" or "cmr")
# 4: gamma_est, for cmr data (real number from 1 to 50) 
# 5: xi.method (NULL or "neural_network")
# 6: compute.jesson (boolean)
# 7: doses.length (2:infty)
# 8: version (1:infty)
commandArgs <- function(...) c(FALSE, 3, "simul", 1, "NULL", TRUE, 2, 4)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(FALSE, 3, "simul", 1, "NULL", TRUE, 3, 5)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(FALSE, 3, "simul", 1, "NULL", TRUE, 4, 6)
source("./sens_analys_MC_cmr_and_simu.R")
```

```{r}
version <- "v4"
version2 <- "v5"
version3 <- "v6"

qb.mc.bounds <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version, ".RData"))
qb.exec.times <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version, ".RData"))
qb.cov <- readRDS(paste0("results/qb_simul_cov_B_100_", version, ".RData"))

jesson.mc.bounds <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version, ".RData"))
jesson.exec.times <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version, ".RData"))
jesson.cov <- readRDS(paste0("results/jesson_simul_cov_B_100_", version, ".RData"))

gammas <- readRDS(paste0("results/gammas_simul_", version, ".RData"))

qb.mc.bounds2 <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version2, ".RData"))
qb.exec.times2 <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version2, ".RData"))
qb.cov2 <- readRDS(paste0("results/qb_simul_cov_B_100_", version2, ".RData"))

jesson.mc.bounds2 <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version2, ".RData"))
jesson.exec.times2 <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version2, ".RData"))
jesson.cov2 <- readRDS(paste0("results/jesson_simul_cov_B_100_", version2, ".RData"))

gammas2 <- readRDS(paste0("results/gammas_simul_", version2, ".RData"))

qb.mc.bounds3 <- readRDS(paste0("results/qb_simul_APO_bounds_B_100_", version3, ".RData"))
qb.exec.times3 <- readRDS(paste0("results/qb_simul_exec_time_B_100_", version3, ".RData"))
qb.cov3 <- readRDS(paste0("results/qb_simul_cov_B_100_", version3, ".RData"))

jesson.mc.bounds3 <- readRDS(paste0("results/jesson_simul_APO_bounds_B_100_", version3, ".RData"))
jesson.exec.times3 <- readRDS(paste0("results/jesson_simul_exec_time_B_100_", version3, ".RData"))
jesson.cov3 <- readRDS(paste0("results/jesson_simul_cov_B_100_", version3, ".RData"))

gammas3 <- readRDS(paste0("results/gammas_simul_", version3, ".RData"))

n.MC <- length(qb.mc.bounds)
doses.length <- length(qb.mc.bounds[[1]]$dose) / 2
quant.order <- 0.99

# Compute the mean coverage for each Monte-Carlo sample
qb.coverage.vec <- rep(NA, n.MC)
jesson.coverage.vec <- rep(NA, n.MC)
# the mean CI length
qb.CI.length.vec <- rep(NA, n.MC)
jesson.CI.length.vec <- rep(NA, n.MC)
# and the mean PEI length
qb.PEI.length.vec <- rep(NA, n.MC)
jesson.PEI.length.vec <- rep(NA, n.MC)

other.qb.df <- NULL
other.jesson.df <- NULL

other.qb.df2 <- NULL
other.jesson.df2 <- NULL

other.qb.df3 <- NULL
other.jesson.df3 <- NULL

for (i in 1:n.MC) {
  
  # For continuous QB
  qb.mc.bounds.i <- qb.mc.bounds[[i]]
  qb.mc.bounds.i.ci <- qb.mc.bounds.i[qb.mc.bounds.i$type == "CI", ]
  qb.mc.bounds.i.pei <- qb.mc.bounds.i[qb.mc.bounds.i$type == "PEI", ]
  
  qb.coverage.vec[i] <- mean(qb.mc.bounds.i.ci$lb <= qb.mc.bounds.i.ci$apo & qb.mc.bounds.i.ci$apo <= qb.mc.bounds.i.ci$ub)
  qb.CI.length.vec[i] <- mean(qb.mc.bounds.i.ci$ub - qb.mc.bounds.i.ci$lb)
  qb.PEI.length.vec[i] <- mean(qb.mc.bounds.i.pei$ub - qb.mc.bounds.i.pei$lb)
  
  qb.mc.bounds.i$MC.ind <- i
  other.qb.df <- rbind(other.qb.df, qb.mc.bounds.i)
  
  qb.mc.bounds.i2 <- qb.mc.bounds2[[i]]
  qb.mc.bounds.i2$MC.ind <- i
  other.qb.df2 <- rbind(other.qb.df2, qb.mc.bounds.i2)

  qb.mc.bounds.i3 <- qb.mc.bounds3[[i]]
  qb.mc.bounds.i3$MC.ind <- i
  other.qb.df3 <- rbind(other.qb.df3, qb.mc.bounds.i3)
  
  # For Jesson
  jesson.mc.bounds.i <- jesson.mc.bounds[[i]]
  jesson.mc.bounds.i.ci <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "CI", ]
  jesson.mc.bounds.i.pei <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "PEI", ]
  
  jesson.coverage.vec[i] <- mean(jesson.mc.bounds.i.ci$lb <= jesson.mc.bounds.i.ci$apo & jesson.mc.bounds.i.ci$apo <= jesson.mc.bounds.i.ci$ub)
  jesson.CI.length.vec[i] <- mean(jesson.mc.bounds.i.ci$ub - jesson.mc.bounds.i.ci$lb)
  jesson.PEI.length.vec[i] <- mean(jesson.mc.bounds.i.pei$ub - jesson.mc.bounds.i.pei$lb)
  
  jesson.mc.bounds.i$MC.ind <- i
  other.jesson.df <- rbind(other.jesson.df, jesson.mc.bounds.i)
  
  jesson.mc.bounds.i2 <- jesson.mc.bounds2[[i]]
  jesson.mc.bounds.i2$MC.ind <- i
  other.jesson.df2 <- rbind(other.jesson.df2, jesson.mc.bounds.i2)

  jesson.mc.bounds.i3 <- jesson.mc.bounds3[[i]]
  jesson.mc.bounds.i3$MC.ind <- i
  other.jesson.df3 <- rbind(other.jesson.df3, jesson.mc.bounds.i3)
}

time.factor <- mean(jesson.exec.times) / mean(qb.exec.times)
print(paste("Our method is on average", signif(time.factor, 2), "times faster than the one from Jesson et al. (2022) for 2 values of treatment of interest."))
```

```{r, fig.width = 5.99, fig.height = 4.58}
# For the evolution of execution time as a function of the number of treatment of interest
exec.time.df1 <- data.frame(time=c(qb.exec.times, jesson.exec.times),
                            algo=c(rep("Proposed method", n.MC), rep("Jesson et al. (2022)", n.MC)),
                            doses.length=rep(2, n.MC))

exec.time.df2 <- data.frame(time=c(qb.exec.times2, jesson.exec.times2),
                            algo=c(rep("Proposed method", n.MC), rep("Jesson et al. (2022)", n.MC)),
                            doses.length=rep(3, n.MC))

exec.time.df3 <- data.frame(time=c(qb.exec.times3, jesson.exec.times3),
                            algo=c(rep("Proposed method", n.MC), rep("Jesson et al. (2022)", n.MC)),
                            doses.length=rep(4, n.MC))

exec.times.df <- rbind(exec.time.df1, exec.time.df2, exec.time.df3)

# png("images/simul_exec_times_3MC.png", units="in", width=5.99, height=4.58, res=400)
exec.time.plot <- ggplot(exec.times.df) +
  geom_boxplot(aes(x=as.factor(doses.length), y=time, color=algo), position=position_dodge(width=0)) +
  scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x),
                labels=trans_format("log10", math_format(10^.x))) +
  theme_linedraw() +
  labs(color="Method", x=TeX(r"(Number of treatments $\tau$)"), y="Execution time (in seconds)") +
  scale_color_manual(values=c(our_method_blue, jesson_red), breaks=c("Proposed method", "Jesson et al. (2022)")) +
  theme(legend.position=c(0.8, 0.35),
        legend.background=element_rect(linewidth=0.3, linetype="solid", colour="black"),
        axis.title.x=element_text(size=12),
        axis.title.y=element_text(size=12),
        axis.text=element_text(size=10),
        legend.text=element_text(size=11),
        legend.title=element_text(size=12))
exec.time.plot
# dev.off()
```

### Exploratory analysis of the values of the sensitivity parameter

As a function of the correlation between $\mathbf{X}$ and $\mathbf{U}$, $\rho_\mathbf{XU}$.
```{r, fig.width = 5.16, fig.height = 4.54}
commandArgs <- function(...) "correlation.prop"
source("./MC_simu_gamma_estim.R")  # This can take a few seconds
gamma.vs.corrXU.plot
```

As a function of $\beta_U$.
```{r, fig.width = 5.16, fig.height = 4.54}
commandArgs <- function(...) "beta_U"
source("./MC_simu_gamma_estim.R")  # This can take a few seconds
gamma.vs.beta_u.plot
```



## Real data

```{r}
# Preprocess the data
data.folder.name <- "data/pm25/"
preprocessed.data <- preprocess.pm2.5.cmr.data(data.folder.name)
unnormalized.data <- preprocessed.data$unnormalized.data  # Get all unnormalized data
```

```{r, fig.width = 7.05, fig.height = 4.73}
# To plot CMR as a function of PM2.5
# png("images/cmr_data.png", units="in", width=7.05, height=4.73, res=400)
ggplot(unnormalized.data, aes(x=PM2.5, y=CMR)) +
  geom_point() +
  theme_linedraw() +
  labs(x=TeX(r"($PM_{2.5}$ ($\mu g/m^3$))"), y=TeX(r"(CMR (annual deaths per 100,000 people))"))
# dev.off()
```


### Sensitivity analysis for 15 values of expositions and 6 values of sensitivity parameter, to compare the proposed methodology to Jesson et al. (2022)

```{r}
# 1: parallel.computation.jesson (boolean)
# 2: n.MC (1:infty)
# 3: data.name ("simul" or "cmr")
# 4: gamma_est, for cmr data (real number from 1 to 50) 
# 5: xi.method (NULL or "neural_network")
# 6: compute.jesson (boolean)
# 7: doses.length (2:infty)
# 8: version (1:infty)
commandArgs <- function(...) c(TRUE, 1, "cmr", 1.01, "NULL", TRUE, 15, 1)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(TRUE, 1, "cmr", 1.25, "NULL", TRUE, 15, 2)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(TRUE, 1, "cmr", 1.5, "NULL", TRUE, 15, 3)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(TRUE, 1, "cmr", 2, "NULL", TRUE, 15, 4)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(TRUE, 1, "cmr", 3, "NULL", TRUE, 15, 5)
source("./sens_analys_MC_cmr_and_simu.R")

commandArgs <- function(...) c(TRUE, 1, "cmr", 50, "NULL", TRUE, 15, 6)
source("./sens_analys_MC_cmr_and_simu.R")
```

```{r}
version <- "v1"
version2 <- "v2"
version3 <- "v3"
version4 <- "v4"
version5 <- "v5"
version6 <- "v6"

qb.mc.bounds <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version, ".RData"))
qb.exec.times <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version, ".RData"))
qb.cov <- readRDS(paste0("results/qb_cmr_cov_B_100_", version, ".RData"))

jesson.mc.bounds <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version, ".RData"))
jesson.exec.times <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version, ".RData"))
jesson.cov <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version, ".RData"))

gammas <- readRDS(paste0("results/gammas_cmr_", version, ".RData"))


qb.mc.bounds2 <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version2, ".RData"))
qb.exec.times2 <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version2, ".RData"))
qb.cov2 <- readRDS(paste0("results/qb_cmr_cov_B_100_", version2, ".RData"))

jesson.mc.bounds2 <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version2, ".RData"))
jesson.exec.times2 <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version2, ".RData"))
jesson.cov2 <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version2, ".RData"))

gammas2 <- readRDS(paste0("results/gammas_cmr_", version2, ".RData"))


qb.mc.bounds3 <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version3, ".RData"))
qb.exec.times3 <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version3, ".RData"))
qb.cov3 <- readRDS(paste0("results/qb_cmr_cov_B_100_", version3, ".RData"))

jesson.mc.bounds3 <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version3, ".RData"))
jesson.exec.times3 <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version3, ".RData"))
jesson.cov3 <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version3, ".RData"))

gammas3 <- readRDS(paste0("results/gammas_cmr_", version3, ".RData"))


qb.mc.bounds4 <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version4, ".RData"))
qb.exec.times4 <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version4, ".RData"))
qb.cov4 <- readRDS(paste0("results/qb_cmr_cov_B_100_", version4, ".RData"))

jesson.mc.bounds4 <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version4, ".RData"))
jesson.exec.times4 <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version4, ".RData"))
jesson.cov4 <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version4, ".RData"))

gammas4 <- readRDS(paste0("results/gammas_cmr_", version4, ".RData"))


qb.mc.bounds5 <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version5, ".RData"))
qb.exec.times5 <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version5, ".RData"))
qb.cov5 <- readRDS(paste0("results/qb_cmr_cov_B_100_", version5, ".RData"))

jesson.mc.bounds5 <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version5, ".RData"))
jesson.exec.times5 <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version5, ".RData"))
jesson.cov5 <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version5, ".RData"))

gammas5 <- readRDS(paste0("results/gammas_cmr_", version5, ".RData"))


qb.mc.bounds6 <- readRDS(paste0("results/qb_cmr_APO_bounds_B_100_", version6, ".RData"))
qb.exec.times6 <- readRDS(paste0("results/qb_cmr_exec_time_B_100_", version6, ".RData"))
qb.cov6 <- readRDS(paste0("results/qb_cmr_cov_B_100_", version6, ".RData"))

jesson.mc.bounds6 <- readRDS(paste0("results/jesson_cmr_APO_bounds_B_100_", version6, ".RData"))
jesson.exec.times6 <- readRDS(paste0("results/jesson_cmr_exec_time_B_100_", version6, ".RData"))
jesson.cov6 <- readRDS(paste0("results/jesson_cmr_cov_B_100_", version6, ".RData"))

gammas6 <- readRDS(paste0("results/gammas_cmr_", version6, ".RData"))
```

```{r}
n.MC <- length(qb.mc.bounds)
doses.length <- length(qb.mc.bounds[[1]]$dose) / 2
quant.order <- 0.99


# Compute the mean coverage for each Monte-Carlo sample
qb.coverage.vec <- rep(NA, n.MC)
jesson.coverage.vec <- rep(NA, n.MC)
# the mean CI length
qb.CI.length.vec <- rep(NA, n.MC)
jesson.CI.length.vec <- rep(NA, n.MC)
# and the mean PEI length
qb.PEI.length.vec <- rep(NA, n.MC)
jesson.PEI.length.vec <- rep(NA, n.MC)

other.qb.df <- NULL
other.jesson.df <- NULL

other.qb.df2 <- NULL
other.jesson.df2 <- NULL

other.qb.df3 <- NULL
other.jesson.df3 <- NULL

other.qb.df4 <- NULL
other.jesson.df4 <- NULL

other.qb.df5 <- NULL
other.jesson.df5 <- NULL

other.qb.df6 <- NULL
other.jesson.df6 <- NULL

for (i in 1:n.MC) {
  
  # For continuous QB
  qb.mc.bounds.i <- qb.mc.bounds[[i]]
  qb.mc.bounds.i.ci <- qb.mc.bounds.i[qb.mc.bounds.i$type == "CI", ]
  qb.mc.bounds.i.pei <- qb.mc.bounds.i[qb.mc.bounds.i$type == "PEI", ]
  
  qb.coverage.vec[i] <- mean(qb.mc.bounds.i.ci$lb <= qb.mc.bounds.i.ci$apo & qb.mc.bounds.i.ci$apo <= qb.mc.bounds.i.ci$ub)
  qb.CI.length.vec[i] <- mean(qb.mc.bounds.i.ci$ub - qb.mc.bounds.i.ci$lb)
  qb.PEI.length.vec[i] <- mean(qb.mc.bounds.i.pei$ub - qb.mc.bounds.i.pei$lb)
  
  qb.mc.bounds.i$MC.ind <- i
  other.qb.df <- rbind(other.qb.df, qb.mc.bounds.i)
  
  qb.mc.bounds.i2 <- qb.mc.bounds2[[i]]
  qb.mc.bounds.i2$MC.ind <- i
  other.qb.df2 <- rbind(other.qb.df2, qb.mc.bounds.i2)

  qb.mc.bounds.i3 <- qb.mc.bounds3[[i]]
  qb.mc.bounds.i3$MC.ind <- i
  other.qb.df3 <- rbind(other.qb.df3, qb.mc.bounds.i3)

  qb.mc.bounds.i4 <- qb.mc.bounds4[[i]]
  qb.mc.bounds.i4$MC.ind <- i
  other.qb.df4 <- rbind(other.qb.df4, qb.mc.bounds.i4)

  qb.mc.bounds.i5 <- qb.mc.bounds5[[i]]
  qb.mc.bounds.i5$MC.ind <- i
  other.qb.df5 <- rbind(other.qb.df5, qb.mc.bounds.i5)

  qb.mc.bounds.i6 <- qb.mc.bounds6[[i]]
  qb.mc.bounds.i6$MC.ind <- i
  other.qb.df6 <- rbind(other.qb.df6, qb.mc.bounds.i6)
  
  # For Jesson
  jesson.mc.bounds.i <- jesson.mc.bounds[[i]]
  jesson.mc.bounds.i.ci <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "CI", ]
  jesson.mc.bounds.i.pei <- jesson.mc.bounds.i[jesson.mc.bounds.i$type == "PEI", ]
  
  jesson.coverage.vec[i] <- mean(jesson.mc.bounds.i.ci$lb <= jesson.mc.bounds.i.ci$apo & jesson.mc.bounds.i.ci$apo <= jesson.mc.bounds.i.ci$ub)
  jesson.CI.length.vec[i] <- mean(jesson.mc.bounds.i.ci$ub - jesson.mc.bounds.i.ci$lb)
  jesson.PEI.length.vec[i] <- mean(jesson.mc.bounds.i.pei$ub - jesson.mc.bounds.i.pei$lb)
  
  jesson.mc.bounds.i$MC.ind <- i
  other.jesson.df <- rbind(other.jesson.df, jesson.mc.bounds.i)
  
  jesson.mc.bounds.i2 <- jesson.mc.bounds2[[i]]
  jesson.mc.bounds.i2$MC.ind <- i
  other.jesson.df2 <- rbind(other.jesson.df2, jesson.mc.bounds.i2)

  jesson.mc.bounds.i3 <- jesson.mc.bounds3[[i]]
  jesson.mc.bounds.i3$MC.ind <- i
  other.jesson.df3 <- rbind(other.jesson.df3, jesson.mc.bounds.i3)

  jesson.mc.bounds.i4 <- jesson.mc.bounds4[[i]]
  jesson.mc.bounds.i4$MC.ind <- i
  other.jesson.df4 <- rbind(other.jesson.df4, jesson.mc.bounds.i4)

  jesson.mc.bounds.i5 <- jesson.mc.bounds5[[i]]
  jesson.mc.bounds.i5$MC.ind <- i
  other.jesson.df5 <- rbind(other.jesson.df5, jesson.mc.bounds.i5)

  jesson.mc.bounds.i6 <- jesson.mc.bounds6[[i]]
  jesson.mc.bounds.i6$MC.ind <- i
  other.jesson.df6 <- rbind(other.jesson.df6, jesson.mc.bounds.i6)
}
```

```{r, fig.width = 10, fig.height = 4.54}
# Colorblind palette
cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#CC79A7", "#0072B2", "#D55E00", "#F0E442")

other.qb.df$gamma <- 1.01
other.qb.df2$gamma <- 1.25
other.qb.df3$gamma <- 1.5
other.qb.df4$gamma <- 2
other.qb.df5$gamma <- 3
other.qb.df6$gamma <- 50

other.jesson.df$gamma <- 1.01
other.jesson.df2$gamma <- 1.25
other.jesson.df3$gamma <- 1.5
other.jesson.df4$gamma <- 2
other.jesson.df5$gamma <- 3
other.jesson.df6$gamma <- 50

ci.data <- rbind(other.qb.df,
                 other.qb.df2,
                 other.qb.df3,
                 other.qb.df4,
                 other.qb.df5,
                 other.qb.df6,
                 other.jesson.df,
                 other.jesson.df2,
                 other.jesson.df3,
                 other.jesson.df4,
                 other.jesson.df5,
                 other.jesson.df6)

ci.data <- ci.data[ci.data$type == "CI", ]
ci.data[ci.data$method == "Continuous SAIPW-QB", ]$method <- "Proposed method"
ci.data[ci.data$method == "Jesson et al.", ]$method <- "Jesson et al. (2022)"

CMR.mean <- mean(unnormalized.data$CMR)

#png("images/cmr_sens_anal_without_gamma_50.png", units="in", width=11.44, height=4.73, res=400)  # height=5.44
cmr.sens.anal.plot <- ggplot(ci.data) +
  geom_point(data=unnormalized.data, aes(x=PM2.5, y=CMR), color="#EEEEEE") +
  geom_line(aes(x=dose, y=lb, linetype=method, color=as.factor(gamma))) +
  geom_line(aes(x=dose, y=ub, linetype=method, color=as.factor(gamma))) +
  geom_hline(yintercept=CMR.mean, linetype="twodash", color="red", alpha=0.7) +  # yintercept=247
  theme_linedraw() +
  scale_color_manual(values=cbp1) +  # colorblind palette
  scale_linetype_manual(name="Method", values=c("solid", "longdash"), breaks=c("Proposed method", "Jesson et al. (2022)")) +
  scale_x_continuous(breaks=unique(ci.data$dose),
                     labels=signif(unique(ci.data$dose), 3),
                     limits=c(3.27-0.5, 7.98+0.5)) +
  labs(color=TeX(r"(Sensitivity parameter \Gamma)"), x=TeX(r"($PM_{2.5}$ ($\mu g / m^3$))"), y=TeX(r"(CMR (annual deaths per 100,000 people))")) +
  annotate("text", x=2.8, y=CMR.mean+8, label=round(CMR.mean, 0), colour="red", alpha=0.7) +
  theme(axis.title.x=element_text(size=14),
        axis.title.y=element_text(size=14),
        axis.text=element_text(size=10),
        legend.text=element_text(size=11),
        legend.title=element_text(size=12)) +
  ylim(100, 430)
cmr.sens.anal.plot
#dev.off()
```































